Scaling up a GF grammar and preparing it for cool stuff for Swedish

### 2011-12-01 doc/report/report.tex
reort

\subsubsection{The resource library}
The resource library\cite{gf-resource} is a very useful part of the framework. It is provided in the 
GF package. %, they give a good start for all who want to write an application grammar.
Instead of letting the users of the framework reimplement the morphological and
the fundamental syntactic structures of a language for each application, all
this can be found as libraries. So far there are 20 languages in the library, and
they all share the same abstract syntax.
The resource grammars describe how to decline words and how to construct
phrases and sentences.
There are also a small test lexicon included, containing some hundered of common words.\\

@@

\section{Saldo}
\label{sec:prog.saldo}
Saldo is compatible with GF, which makes it easy to transform the morphological
lexicon into our format. The lexicon has been imported earlier (Krasimir,2009?)
but the code needed updates to not miss many important words.
Experiments have been made to use a interactive tool for lexical aquisation,
but the dictionary was still much to small. The aquisation tool may still
be used for complenting the lexicon.

>>>>

\subsubsection{The resource library}
The resource library\cite{gf-resource} is a very useful part of the framework. It is provided in the 
GF package. %, they give a good start for all who want to write an application grammar.
Instead of letting the users of the framework reimplement the morphological and
the fundamental syntactic structures of a language for each application, all
this can be found as libraries. So far there are 20 languages in the library, and
they all share the same abstract syntax.
The resource grammars describe how to construct phrases and sentences and how to
decline words. The latter is done by smart paradigms: functions that analyses
some given forms of a word to find out how the inflection table should look.
For example, the declination of many Swedish nouns can be determined by looking
at the singular form only. This is the case for ``flicka"??, the correct declination
can be guessed by noting that the word ends with an ``a". Like most Swedish nouns
ending with an ``a", it follows the first?? declination. For others, like
"hjärta", also the plural form "hjärtan" is needed, even though it ends
with an ``a". The worst case is nouns that need four forms, both singular and
plural in definite and indefinite form.
There are also a small test lexicon included, containing some hundered of common words.\\

@@

\section{Importing Saldo}
\label{sec:prog.saldo}
Saldo is compatible with GF, which makes it easy to transform the morphological
lexicon into our format. The lexicon has been imported earlier (Krasimir,2009?)
but the code needed updates to not miss many important words.
Experiments have been made to use a interactive tool for lexical aquisation,
but the dictionary was still much to small. The aquisation tool may still
be used for complenting the lexicon.
